Adversarial Zero-Shot Learning

### 2017-11-17 doc/paper.tex
Added dataset

\section{Datasets}

	Datasets we use.

>>>>

\section{Data}

	We use two datasets: The Caltech-UCSD Birds 200 (2010) dataset \cite{Welinder2010}, and the Oxford VGG 102 category flower dataset \cite{Nilsback2008}. The Birds dataset has class number 200, feature dimension 500 $\times$ [300--500] $\times$ 3, and the size of the dataset is 6033. The bird images belonging to 200 species. Each class consists of between 20 and 40 images, with total of 6033 color images in jpeg format.

	The Oxford VGG 102 category flower dataset has class number 102, feature dimension [500--600] $\times$ 500 $\times$ 3, and the size of the dataset is 8189. The flower images belonging to 102 categories. Each class consists of between 40 and 258 images, with total of 8189 color images in jpeg format.
